### 2020-05-30 writeup/experiments.tex
sec 4.3

\textbf{A Metric to determine positive or negative Transfer.}
We validate the metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer based on STL results.
Table \ref{tab:mtl_better_than_stl} shows that using a threshold of $0.1$, we can predict $75.6\%$ among 150 task pairs for the sentiment analysis tasks with $38.8\%$ recall.
Similar for 91 image classification task pairs.
Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14, the training data size is 10,000.

@@

\textbf{Improving labeled data efficiency.}
We measure the data efficiency ratio on the sentiment analysis tasks.
We find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks.
If TREC is not included, we see that only $25\%$ of the labeled data is needed.

>>>>

\textbf{A metric to determine positive or negative transfer.}
We validate the metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer based on STL results.
Table \ref{tab:mtl_better_than_stl} shows that using a threshold of $0.1$, we can predict $75.6\%$ among 150 task pairs for the sentiment analysis tasks with $38.8\%$ recall.
Similar for 91 image classification task pairs.
Note: For text classification tasks, the source task training data size ranges from 500 to 1,500 and target task training data size is 1000; For ChestX-ray14, the training data size is 10,000.

@@

\textbf{MTL improves labeled data efficiency.}
We measure the data efficiency ratio on the sentiment analysis tasks.
We find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks.
If TREC is not included, we see that only $25\%$ of the labeled data is needed.
